---
title: "SA app user data Latin America 1Dec20-1Jan22"
author: "Dani Behonick"
date: "2/2/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("readr")
install.packages("dplyr")
install.packages("ggplot2")
library(readr)
library(dplyr)
library(ggplot2)
```
*NEW USERS*
```{r}
LAnewusers_Dec20Jan22 <- read.csv("newusers_20201201to20220101.csv",
skip = 1, head = FALSE, sep = ",")
```

*Data cleaning*
```{r}
#columns renamed
colnames(LAnewusers_Dec20Jan22) <- c("Country_ID", "2021_01",
"2020_12", "2021_06", "2021_11", "2021_05", "2021_02", "2021_08",
"2021_12", "2021_07", "2021_10", "2021_09", "2021_04", "2021_03",
"2022_01", "Totals")

#header rows and data entries for non-Wyss LA countries removed
LAnewusers_Dec20Jan22 <- LAnewusers_Dec20Jan22 %>%
filter(Country_ID == "MX" | Country_ID == "AR" | Country_ID == "CO" |
Country_ID == "GT" | Country_ID == "HN" | Country_ID == "PE" |
Country_ID == "EC")

#transposed rows/columns
LAnewusers_Dec20Jan22_2 <- t(LAnewusers_Dec20Jan22[-1])
colnames(LAnewusers_Dec20Jan22_2) <- LAnewusers_Dec20Jan22[, 1]

#making time a recognized column variable
LAnewusers_Dec20Jan22_2 <- cbind(rownames(LAnewusers_Dec20Jan22_2), 
  LAnewusers_Dec20Jan22_2)
rownames(LAnewusers_Dec20Jan22_2) <- NULL

#Totals row removed
LAnewusers_Dec20Jan22_2 <- LAnewusers_Dec20Jan22_2[-c(15), ]

#make it a dataframe
LAnewusers_Dec20Jan22_2 <- as.data.frame(LAnewusers_Dec20Jan22_2)
```

```{r}
install.packages("tidyr")
library(tidyr)
```
```{r}
#pivot to make CountryID a callable variable
LAnewusers_Dec20Jan22_3 <- pivot_longer(LAnewusers_Dec20Jan22_2, cols=2:8, names_to = "Country", values_to = "New_users")

#rename columns
colnames(LAnewusers_Dec20Jan22_3) <- c("Year_Month","CountryID","New_Users")

#make it a dataframe
LAnewusers_Dec20Jan22_3 <- as.data.frame(LAnewusers_Dec20Jan22_3)
```

```{r}
#coerce New_Users to numeric variable rather than character
typeof(LAnewusers_Dec20Jan22_3$New_Users)
LAnewusers_Dec20Jan22_3$New_Users <- as.numeric(LAnewusers_Dec20Jan22_3$New_Users)
typeof(LAnewusers_Dec20Jan22_3$New_Users)

#make Month_Year a date/time object
install.packages("zoo")
library(zoo)
Year_Month <- LAnewusers_Dec20Jan22_3$Year_Month
Year_Month_2 <- as.yearmon(as.character(Year_Month), "%Y_%m")
LAnewusers_Dec20Jan22_3[ , 'Year_Month'] <- Year_Month_2
typeof(LAnewusers_Dec20Jan22_3$Year_Month)
```
Complete January 2022 analytics data available now! (Previous analysis done mid-January with incomplete data) Let's merge that in ...
```{r}
LAnewusers_Jan22Feb22 <- read.csv("newusers_20220101to202220201.csv",
skip = 1, head = FALSE, sep = ",")

colnames(LAnewusers_Jan22Feb22) <- c("Country_ID", "2022_01",
"2022_02", "Totals")

LAnewusers_Jan22Feb22 <- LAnewusers_Jan22Feb22 %>%
filter(Country_ID == "MX" | Country_ID == "AR" | Country_ID == "CO" |
Country_ID == "GT" | Country_ID == "HN" | Country_ID == "PE" |
Country_ID == "EC")

LAnewusers_Jan22Feb22_2 <- t(LAnewusers_Jan22Feb22[-1])
colnames(LAnewusers_Jan22Feb22_2) <- c("MX", "AR", "EC", "PE", "CO", "GT", "HN")

#making time a recognized column variable
LAnewusers_Jan22Feb22_2 <- cbind(rownames(LAnewusers_Jan22Feb22_2), 
  LAnewusers_Jan22Feb22_2)
rownames(LAnewusers_Jan22Feb22_2) <- NULL

LAnewusers_Jan22Feb22_2 <- LAnewusers_Jan22Feb22_2[-c(3), ]

LAnewusers_Jan22Feb22_2 <- as.data.frame(LAnewusers_Jan22Feb22_2)

LAnewusers_Jan22Feb22_3 <- pivot_longer(LAnewusers_Jan22Feb22_2, cols=2:8, names_to = "Country", values_to = "New_users")

colnames(LAnewusers_Jan22Feb22_3) <- c("Year_Month","CountryID","New_Users")

LAnewusers_Jan22Feb22_3 <- as.data.frame(LAnewusers_Jan22Feb22_3)

LAnewusers_Jan22Feb22_3$New_Users <- as.numeric(LAnewusers_Jan22Feb22_3$New_Users)

Year_MonthJanFeb <- LAnewusers_Jan22Feb22_3$Year_Month
Year_MonthJanFeb_2 <- as.yearmon(as.character(Year_MonthJanFeb), "%Y_%m")
LAnewusers_Jan22Feb22_3[ , 'Year_Month'] <- Year_MonthJanFeb_2
typeof(LAnewusers_Jan22Feb22_3$Year_Month)

LAnewusers_Jan22 <- LAnewusers_Jan22Feb22_3 %>% filter(Year_Month == "Jan 2022")

LAnewusers_Dec20Dec21 <- LAnewusers_Dec20Jan22_3 %>% filter(Year_Month != "Jan 2022")


LAnewusers_Dec20Jan22full <- rbind(LAnewusers_Dec20Dec21, LAnewusers_Jan22)
```

```{r}
#jpeg('LAnewusers_Dec20Jan22_3.jpg')
#ggplot(data = LAnewusers_Dec20Jan22_3, aes(x=Year_Month, y=New_Users)) + 
  #geom_line(aes(color=CountryID)) + labs(x = "Time", y = "New Users", 
  #title = "Total new users, LA Wyss countries, 2020Dec-2022Jan") + 
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

#jpeg('LAnewusers_Dec20Jan22full.jpg')
ggplot(data = LAnewusers_Dec20Jan22full, aes(x=Year_Month, y=New_Users)) + 
  geom_line(aes(color=CountryID)) + labs(x = "Time", y = "New Users", 
  title = "New users, LA Wyss countries, 2020Dec-2022Jan") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```
*RETURN USERS*
```{r}
LAreturningusers_Dec20Jan22 <- read.csv("returningusers_20201201to20220101.csv",
skip = 1, head = FALSE, sep = ",")
```

*Data cleaning*
```{r}
#columns renamed
colnames(LAreturningusers_Dec20Jan22) <- c("Country_ID", "2021_01",
"2020_12", "2021_02", "2021_05", "2021_06", "2021_04", "2021_03",
"2021_12", "2021_10", "2021_07", "2021_11", "2021_09", "2022_01", "Totals")

#header rows and data entries for non-Wyss LA countries removed
LAreturningusers_Dec20Jan22 <- LAreturningusers_Dec20Jan22 %>%
filter(Country_ID == "MX" | Country_ID == "AR" | Country_ID == "CO" |
Country_ID == "GT" | Country_ID == "HN" | Country_ID == "PE" |
Country_ID == "EC")

#transposed rows/columns
LAreturningusers_Dec20Jan22_2 <- t(LAreturningusers_Dec20Jan22[-1])
colnames(LAreturningusers_Dec20Jan22_2) <- LAreturningusers_Dec20Jan22[, 1]

#making time a recognized column variable
LAreturningusers_Dec20Jan22_2 <- cbind(rownames(LAreturningusers_Dec20Jan22_2), 
  LAreturningusers_Dec20Jan22_2)
rownames(LAreturningusers_Dec20Jan22_2) <- NULL

#Totals row removed
LAreturningusers_Dec20Jan22_2 <- LAreturningusers_Dec20Jan22_2[-c(14), ]

#make it a dataframe
LAreturningusers_Dec20Jan22_2 <- as.data.frame(LAreturningusers_Dec20Jan22_2)

#pivot to make CountryID a callable variable
LAreturningusers_Dec20Jan22_3 <- pivot_longer(LAreturningusers_Dec20Jan22_2, cols=2:8, names_to = "Country", values_to = "Returning_users")

#rename columns
colnames(LAreturningusers_Dec20Jan22_3) <- c("Year_Month","CountryID","Returning_Users")

#make it a dataframe
LAreturningusers_Dec20Jan22_3 <- as.data.frame(LAreturningusers_Dec20Jan22_3)

#coerce Returning_Users to numeric variable rather than character
LAreturningusers_Dec20Jan22_3$Returning_Users <- as.numeric(LAreturningusers_Dec20Jan22_3$Returning_Users)
typeof(LAreturningusers_Dec20Jan22_3$Returning_Users)

#make Month_Year a date/time object
Year_Month_returning <- LAreturningusers_Dec20Jan22_3$Year_Month
Year_Month_returning_2 <- as.yearmon(as.character(Year_Month_returning), "%Y_%m")
LAreturningusers_Dec20Jan22_3[ , 'Year_Month'] <- Year_Month_returning_2
typeof(LAreturningusers_Dec20Jan22_3$Year_Month)

#jpeg('LAreturningusers_Dec20Jan22_3.jpg')
#ggplot(data = LAreturningusers_Dec20Jan22_3, aes(x=Year_Month, y=Returning_Users)) + 
  #geom_line(aes(color=CountryID)) + labs(x = "Year_Month", y = "Returning Users", 
  #title = "Total returning users, LA Wyss countries, 2020Dec-2022Jan") + 
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```
Merging in completed Jan 2022 analytics data ...
```{r}
LAreturningusers_Jan22Feb22 <- read.csv("returningusers_20220101to20220201.csv",
skip = 1, head = FALSE, sep = ",")

colnames(LAreturningusers_Jan22Feb22) <- c("Country_ID", "2022_01",
"2022_02", "Totals")

LAreturningusers_Jan22Feb22 <- LAreturningusers_Jan22Feb22 %>%
filter(Country_ID == "MX" | Country_ID == "AR" | Country_ID == "CO" |
Country_ID == "GT" | Country_ID == "HN" | Country_ID == "PE" |
Country_ID == "EC")

LAreturningusers_Jan22Feb22_2 <- t(LAreturningusers_Jan22Feb22[-1])
colnames(LAreturningusers_Jan22Feb22_2) <- c("AR", "CO", "EC", "GT", "HN", "MX", "PE")

LAreturningusers_Jan22Feb22_2 <- cbind(rownames(LAreturningusers_Jan22Feb22_2), 
  LAreturningusers_Jan22Feb22_2)
rownames(LAreturningusers_Jan22Feb22_2) <- NULL

LAreturningusers_Jan22Feb22_2 <- LAreturningusers_Jan22Feb22_2[-c(3), ]

LAreturningusers_Jan22Feb22_2 <- as.data.frame(LAreturningusers_Jan22Feb22_2)

LAreturningusers_Jan22Feb22_3 <- pivot_longer(LAreturningusers_Jan22Feb22_2, cols=2:8, names_to = "Country", values_to = "Returning_users")

colnames(LAreturningusers_Jan22Feb22_3) <- c("Year_Month","CountryID","Returning_Users")

LAreturningusers_Jan22Feb22_3 <- as.data.frame(LAreturningusers_Jan22Feb22_3)

LAreturningusers_Jan22Feb22_3$Returning_Users <- as.numeric(LAreturningusers_Jan22Feb22_3$Returning_Users)

Year_MonthJanFebRet <- LAreturningusers_Jan22Feb22_3$Year_Month
Year_MonthJanFebRet_2 <- as.yearmon(as.character(Year_MonthJanFebRet), "%Y_%m")
LAreturningusers_Jan22Feb22_3[ , 'Year_Month'] <- Year_MonthJanFebRet_2
typeof(LAreturningusers_Jan22Feb22_3$Year_Month)

LAreturningusers_Jan22 <- LAreturningusers_Jan22Feb22_3 %>% filter(Year_Month == "Jan 2022")

LAreturningusers_Dec20Dec21 <- LAreturningusers_Dec20Jan22_3 %>% filter(Year_Month != "Jan 2022")

LAreturningusers_Dec20Jan22full <- rbind(LAreturningusers_Dec20Dec21, LAreturningusers_Jan22)

#jpeg('LAreturningusers_Dec20Jan22full.jpg')
ggplot(data = LAreturningusers_Dec20Jan22full, aes(x=Year_Month, y=Returning_Users)) + 
  geom_line(aes(color=CountryID)) + labs(x = "Time", y = "Returning Users", 
  title = "Returning users, LA Wyss countries, 2020Dec-2022Jan") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```


*TOTAL USERS*
Note: analysis done with incomplete analytics data for Jan2022
```{r}
LAtotalusers_Dec20Jan22 <- read.csv("totalusers_20201201to20220101.csv",
skip = 1, head = FALSE, sep = ",")
```

*Data cleaning*
```{r}
#columns renamed
colnames(LAtotalusers_Dec20Jan22) <- c("Country_ID", "2021_01",
"2020_12", "2021_02", "2021_08", "2021_12", "2021_11", "2021_06",
"2021_07", "2021_05", "2021_09", "2021_10", "2021_04", "2021_03", "2022_01", "Totals")

#header rows and data entries for non-Wyss LA countries removed
LAtotalusers_Dec20Jan22 <- LAtotalusers_Dec20Jan22 %>%
filter(Country_ID == "MX" | Country_ID == "AR" | Country_ID == "CO" |
Country_ID == "GT" | Country_ID == "HN" | Country_ID == "PE" |
Country_ID == "EC")

#transposed rows/columns
LAtotalusers_Dec20Jan22_2 <- t(LAtotalusers_Dec20Jan22[-1])
colnames(LAtotalusers_Dec20Jan22_2) <- LAtotalusers_Dec20Jan22[, 1]

#making time a recognized column variable
LAtotalusers_Dec20Jan22_2 <- cbind(rownames(LAtotalusers_Dec20Jan22_2), 
  LAtotalusers_Dec20Jan22_2)
rownames(LAtotalusers_Dec20Jan22_2) <- NULL

#Totals row removed
LAtotalusers_Dec20Jan22_2 <- LAtotalusers_Dec20Jan22_2[-c(15), ]

#make it a dataframe
LAtotalusers_Dec20Jan22_2 <- as.data.frame(LAtotalusers_Dec20Jan22_2)

#pivot to make CountryID a callable variable
LAtotalusers_Dec20Jan22_3 <- pivot_longer(LAtotalusers_Dec20Jan22_2, cols=2:8, names_to = "Country", values_to = "Total_users")

#rename columns
colnames(LAtotalusers_Dec20Jan22_3) <- c("Year_Month","CountryID","Total_Users")

#make it a dataframe
LAtotalusers_Dec20Jan22_3 <- as.data.frame(LAtotalusers_Dec20Jan22_3)

#coerce Total_Users to numeric variable rather than character
LAtotalusers_Dec20Jan22_3$Total_Users <- as.numeric(LAtotalusers_Dec20Jan22_3$Total_Users)
typeof(LAtotalusers_Dec20Jan22_3$Total_Users)

#make Month_Year a date/time object
Year_Month_total <- LAtotalusers_Dec20Jan22_3$Year_Month
Year_Month_total_2 <- as.yearmon(as.character(Year_Month_total), "%Y_%m")
LAtotalusers_Dec20Jan22_3[ , 'Year_Month'] <- Year_Month_total_2
typeof(LAtotalusers_Dec20Jan22_3$Year_Month)

#jpeg('LAtotalusers_Dec20Jan22_3.jpg')
ggplot(data = LAtotalusers_Dec20Jan22_3, aes(x=Year_Month, y=Total_Users)) + 
  geom_line(aes(color=CountryID)) + labs(x = "Year_Month", y = "Total Users", 
  title = "Total users, LA Wyss countries, 2020Dec-2022Jan") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

*PREDICTING FUTURE USE*
New users, MX
```{r, New users MX}
LAnewusers_Dec20Jan22_3_MX <- LAnewusers_Dec20Jan22_3 %>% filter(CountryID == "MX")

newusers_MX_lm <- lm(New_Users~Year_Month, LAnewusers_Dec20Jan22_3_MX)

New_dates <- data.frame(Year_Month= c("2022_04", "2022_07"))
New_Year_Month <- New_dates$Year_Month
New_Year_Month_2 <- as.yearmon(as.character(New_Year_Month), "%Y_%m")
New_dates[ , 'Year_Month'] <- New_Year_Month_2
typeof(New_dates$Year_Month)

New_users_prediction_col_MX <- predict(newusers_MX_lm, New_dates)
New_users_prediction_MX <- cbind(New_dates, New_users_prediction_col_MX)
```

New users, AR
```{r, New users AR}
LAnewusers_Dec20Jan22_3_AR <- LAnewusers_Dec20Jan22_3 %>% filter(CountryID == "AR")

newusers_AR_lm <- lm(New_Users~Year_Month, LAnewusers_Dec20Jan22_3_AR)

New_users_prediction_col_AR <- predict(newusers_AR_lm, New_dates)
New_users_prediction_AR <- cbind(New_dates, New_users_prediction_col_AR)
```

New users, CO
```{r, New users CO}
LAnewusers_Dec20Jan22_3_CO <- LAnewusers_Dec20Jan22_3 %>% filter(CountryID == "CO")

newusers_CO_lm <- lm(New_Users~Year_Month, LAnewusers_Dec20Jan22_3_CO)

New_users_prediction_col_CO <- predict(newusers_CO_lm, New_dates)
New_users_prediction_CO <- cbind(New_dates, New_users_prediction_col_CO)
```

New users, GT
```{r, New users GT}
LAnewusers_Dec20Jan22_3_GT <- LAnewusers_Dec20Jan22_3 %>% filter(CountryID == "GT")

newusers_GT_lm <- lm(New_Users~Year_Month, LAnewusers_Dec20Jan22_3_GT)

New_users_prediction_col_GT <- predict(newusers_GT_lm, New_dates)
New_users_prediction_GT <- cbind(New_dates, New_users_prediction_col_GT)
```

New users, HN
```{r, New users HN}
LAnewusers_Dec20Jan22_3_HN <- LAnewusers_Dec20Jan22_3 %>% filter(CountryID == "HN")

newusers_HN_lm <- lm(New_Users~Year_Month, LAnewusers_Dec20Jan22_3_HN)

New_users_prediction_col_HN <- predict(newusers_HN_lm, New_dates)
New_users_prediction_HN <- cbind(New_dates, New_users_prediction_col_HN)
```

New users, PE
```{r, New users PE}
LAnewusers_Dec20Jan22_3_PE <- LAnewusers_Dec20Jan22_3 %>% filter(CountryID == "PE")

newusers_PE_lm <- lm(New_Users~Year_Month, LAnewusers_Dec20Jan22_3_PE)

New_users_prediction_col_PE <- predict(newusers_PE_lm, New_dates)
New_users_prediction_PE <- cbind(New_dates, New_users_prediction_col_PE)
```

New users, EC
```{r, New users EC}
LAnewusers_Dec20Jan22_3_EC <- LAnewusers_Dec20Jan22_3 %>% filter(CountryID == "EC")

newusers_EC_lm <- lm(New_Users~Year_Month, LAnewusers_Dec20Jan22_3_EC)

New_users_prediction_col_EC <- predict(newusers_EC_lm, New_dates)
New_users_prediction_EC <- cbind(New_dates, New_users_prediction_col_EC)
```

```{r}
New_users_prediction <- cbind(New_dates, New_users_prediction_AR$New_users_prediction_col_AR, New_users_prediction_CO$New_users_prediction_col_CO, New_users_prediction_EC$New_users_prediction_col_EC, New_users_prediction_GT$New_users_prediction_col_GT, New_users_prediction_HN$New_users_prediction_col_HN, New_users_prediction_MX$New_users_prediction_col_MX, New_users_prediction_PE$New_users_prediction_col_PE)

colnames(New_users_prediction) <- c("Time", "New users prediction AR", "New users prediction CO", "New users prediction EC", "New users prediction GT", "New users prediction HN", "New users prediction MX", "New users prediction PE")

write.csv(New_users_prediction, "New_users_predictionLA.csv")
```


Returning users, MX
```{r, Returning users MX}
LAreturningusers_Dec20Jan22_3_MX <- LAreturningusers_Dec20Jan22_3 %>% filter(CountryID == "MX")

returningusers_MX_lm <- lm(Returning_Users~Year_Month, LAreturningusers_Dec20Jan22_3_MX)

Returning_users_prediction_col_MX <- predict(returningusers_MX_lm, New_dates)
Returning_users_prediction_MX <- cbind(New_dates, Returning_users_prediction_col_MX)
```

Returning users, AR
```{r, Returning users AR}
LAreturningusers_Dec20Jan22_3_AR <- LAreturningusers_Dec20Jan22_3 %>% filter(CountryID == "AR")

returningusers_AR_lm <- lm(Returning_Users~Year_Month, LAreturningusers_Dec20Jan22_3_AR)

Returning_users_prediction_col_AR <- predict(returningusers_AR_lm, New_dates)
Returning_users_prediction_AR <- cbind(New_dates, Returning_users_prediction_col_AR)
```

Returning users, CO
```{r, Returning users CO}
LAreturningusers_Dec20Jan22_3_CO <- LAreturningusers_Dec20Jan22_3 %>% filter(CountryID == "CO")

returningusers_CO_lm <- lm(Returning_Users~Year_Month, LAreturningusers_Dec20Jan22_3_CO)

Returning_users_prediction_col_CO <- predict(returningusers_CO_lm, New_dates)
Returning_users_prediction_CO <- cbind(New_dates, Returning_users_prediction_col_CO)
```

Returning users, GT
```{r, Returning users GT}
LAreturningusers_Dec20Jan22_3_GT <- LAreturningusers_Dec20Jan22_3 %>% filter(CountryID == "GT")

returningusers_GT_lm <- lm(Returning_Users~Year_Month, LAreturningusers_Dec20Jan22_3_GT)

Returning_users_prediction_col_GT <- predict(returningusers_GT_lm, New_dates)
Returning_users_prediction_GT <- cbind(New_dates, Returning_users_prediction_col_GT)
```

Returning users, HN
```{r, Returning users HN}
LAreturningusers_Dec20Jan22_3_HN <- LAreturningusers_Dec20Jan22_3 %>% filter(CountryID == "HN")

returningusers_HN_lm <- lm(Returning_Users~Year_Month, LAreturningusers_Dec20Jan22_3_HN)

Returning_users_prediction_col_HN <- predict(returningusers_HN_lm, New_dates)
Returning_users_prediction_HN <- cbind(New_dates, Returning_users_prediction_col_HN)
```

Returning users, PE
```{r, Returning users PE}
LAreturningusers_Dec20Jan22_3_PE <- LAreturningusers_Dec20Jan22_3 %>% filter(CountryID == "PE")

returningusers_PE_lm <- lm(Returning_Users~Year_Month, LAreturningusers_Dec20Jan22_3_PE)

Returning_users_prediction_col_PE <- predict(returningusers_PE_lm, New_dates)
Returning_users_prediction_PE <- cbind(New_dates, Returning_users_prediction_col_PE)
```

Returning users, EC
```{r, Returning users EC}
LAreturningusers_Dec20Jan22_3_EC <- LAreturningusers_Dec20Jan22_3 %>% filter(CountryID == "EC")

returningusers_EC_lm <- lm(Returning_Users~Year_Month, LAreturningusers_Dec20Jan22_3_EC)

Returning_users_prediction_col_EC <- predict(returningusers_EC_lm, New_dates)
Returning_users_prediction_EC <- cbind(New_dates, Returning_users_prediction_col_EC)
```

```{r}
Returning_users_prediction <- cbind(New_dates, Returning_users_prediction_AR$Returning_users_prediction_col_AR, Returning_users_prediction_CO$Returning_users_prediction_col_CO, Returning_users_prediction_EC$Returning_users_prediction_col_EC, Returning_users_prediction_GT$Returning_users_prediction_col_GT, Returning_users_prediction_HN$Returning_users_prediction_col_HN, Returning_users_prediction_MX$Returning_users_prediction_col_MX, Returning_users_prediction_PE$Returning_users_prediction_col_PE)

colnames(Returning_users_prediction) <- c("Time", "Returning users prediction AR", "Returning users prediction CO", "Returning users prediction EC", "Returning users prediction GT", "Returning users prediction HN", "Returning users prediction MX", "Returning users prediction PE")

write.csv(Returning_users_prediction, "Returning_users_predictionLA.csv")
```

Total users, MX
```{r, Total users MX}
LAtotalusers_Dec20Jan22_3_MX <- LAtotalusers_Dec20Jan22_3 %>% filter(CountryID == "MX")

totalusers_MX_lm <- lm(Total_Users~Year_Month, LAtotalusers_Dec20Jan22_3_MX)

Total_users_prediction_col_MX <- predict(totalusers_MX_lm, New_dates)
Total_users_prediction_MX <- cbind(New_dates, Total_users_prediction_col_MX)
```

Total users, AR
```{r, Total users AR}
LAtotalusers_Dec20Jan22_3_AR <- LAtotalusers_Dec20Jan22_3 %>% filter(CountryID == "AR")

totalusers_AR_lm <- lm(Total_Users~Year_Month, LAtotalusers_Dec20Jan22_3_AR)

Total_users_prediction_col_AR <- predict(totalusers_AR_lm, New_dates)
Total_users_prediction_AR <- cbind(New_dates, Total_users_prediction_col_AR)
```

Total users, CO
```{r, Total users CO}
LAtotalusers_Dec20Jan22_3_CO <- LAtotalusers_Dec20Jan22_3 %>% filter(CountryID == "CO")

totalusers_CO_lm <- lm(Total_Users~Year_Month, LAtotalusers_Dec20Jan22_3_CO)

Total_users_prediction_col_CO <- predict(totalusers_CO_lm, New_dates)
Total_users_prediction_CO <- cbind(New_dates, Total_users_prediction_col_CO)
```

Total users, GT
```{r, Total users GT}
LAtotalusers_Dec20Jan22_3_GT <- LAtotalusers_Dec20Jan22_3 %>% filter(CountryID == "GT")

totalusers_GT_lm <- lm(Total_Users~Year_Month, LAtotalusers_Dec20Jan22_3_GT)

Total_users_prediction_col_GT <- predict(totalusers_GT_lm, New_dates)
Total_users_prediction_GT <- cbind(New_dates, Total_users_prediction_col_GT)
```

Total users, HN
```{r, Total users HN}
LAtotalusers_Dec20Jan22_3_HN <- LAtotalusers_Dec20Jan22_3 %>% filter(CountryID == "HN")

totalusers_HN_lm <- lm(Total_Users~Year_Month, LAtotalusers_Dec20Jan22_3_HN)

Total_users_prediction_col_HN <- predict(totalusers_HN_lm, New_dates)
Total_users_prediction_HN <- cbind(New_dates, Total_users_prediction_col_HN)
```

Total users, PE
```{r, Total users PE}
LAtotalusers_Dec20Jan22_3_PE <- LAtotalusers_Dec20Jan22_3 %>% filter(CountryID == "PE")

totalusers_PE_lm <- lm(Total_Users~Year_Month, LAtotalusers_Dec20Jan22_3_PE)

Total_users_prediction_col_PE <- predict(totalusers_PE_lm, New_dates)
Total_users_prediction_PE <- cbind(New_dates, Total_users_prediction_col_PE)
```

Total users, EC
```{r, Total users EC}
LAtotalusers_Dec20Jan22_3_EC <- LAtotalusers_Dec20Jan22_3 %>% filter(CountryID == "EC")

totalusers_EC_lm <- lm(Total_Users~Year_Month, LAtotalusers_Dec20Jan22_3_EC)

Total_users_prediction_col_EC <- predict(totalusers_EC_lm, New_dates)
Total_users_prediction_EC <- cbind(New_dates, Total_users_prediction_col_EC)
```

```{r}
Total_users_prediction <- cbind(New_dates, Total_users_prediction_AR$Total_users_prediction_col_AR, Total_users_prediction_CO$Total_users_prediction_col_CO, Total_users_prediction_EC$Total_users_prediction_col_EC, Total_users_prediction_GT$Total_users_prediction_col_GT, Total_users_prediction_HN$Total_users_prediction_col_HN, Total_users_prediction_MX$Total_users_prediction_col_MX, Total_users_prediction_PE$Total_users_prediction_col_PE)

colnames(Total_users_prediction) <- c("Time", "Total users prediction AR", "Total users prediction CO", "Total users prediction EC", "Total users prediction GT", "Total users prediction HN", "Total users prediction MX", "Total users prediction PE")

write.csv(Total_users_prediction, "Total_users_predictionLA.csv")
```

*Data analysis & predictions since SM handle change (August 2021)*
```{r}
LAnewusers_Aug21Jan22 <- LAnewusers_Dec20Jan22_3 %>% filter(Year_Month == "Aug 2021" | Year_Month == "Sep 2021" | Year_Month == "Oct 2021" | Year_Month == "Nov 2021" | Year_Month == "Dec 2021" | Year_Month == "Jan 2022")

LAreturningusers_Aug21Jan22 <- LAreturningusers_Dec20Jan22_3 %>% filter(Year_Month == "Aug 2021" | Year_Month == "Sep 2021" | Year_Month == "Oct 2021" | Year_Month == "Nov 2021" | Year_Month == "Dec 2021" | Year_Month == "Jan 2022")

#jpeg('LAnewusers_Aug21Jan22.jpg')
ggplot(data = LAnewusers_Aug21Jan22, aes(x=Year_Month, y=New_Users)) + 
  geom_line(aes(color=CountryID)) + labs(x = "Time", y = "New Users", 
  title = "New users, LA Wyss countries, 2021Aug-2022Jan") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

#jpeg('LAreturningusers_Aug21Jan22.jpg')
ggplot(data = LAreturningusers_Aug21Jan22, aes(x=Year_Month, y=Returning_Users)) + 
  geom_line(aes(color=CountryID)) + labs(x = "Time", y = "Returning Users", 
  title = "Returning users, LA Wyss countries, 2021Aug-2022Jan") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

